\chapter{Introduction}\label{ch:introduction}

%
% Section: History and Background of Local Brand X
%
\section{History and Background of Local Brand X}\label{sec:intro:background}

Local Brand X, an innovative company founded in 2018 and based in Mainz, specializes in marketing management software. The company focuses on industries such as insurance, franchises, insurance, and retail. Local Brand X has developed the Local Marketing Platform, a tool designed to assist businesses in supporting their sales or distribution partners with the creation and execution of marketing initiatives throughout the customer journey. The primary objective of this platform is to ensure consistent local marketing, enhance local visibility, and thereby strengthen the brand. Currently, over 50,000 users from prominent brands such as Audio Service, BayWa, BBBank, and HanseMerkur utilize solutions provided by Local Brand X\cite{Local_Brand_X_AboutUs}.

The Local Marketing Platform facilitates the planning, creation, and implementation of local marketing measures and campaigns by sales partners. It supports cross-media local marketing, including online, social media, print, and video marketing, enabling a diverse range of advertising activities with minimal prior knowledge required. The platform ensures seamless compliance with corporate design and allows for uniform campaign and budget planning across the company and brand. Automated processing of local marketing measures frees up time and resources at the head office for strategic planning and design, enhancing overall company awareness and success\cite{Local_Marketing_Platform_2022}. The Local Marketing Platform's modular structure and the expansion options provided by Local Brand X add-ons enable it to adapt to varying needs and marketing priorities.

%
% Section: Problem Statement
%
\section{Problem Statement}\label{sec:intro:problem_statement}
In today's digital era, users frequently interact with a multitude of web applications and services, each with unique interfaces and login requirements. This results in fragmented workflows and decreased productivity as users navigate between different platforms. Specifically, integrating data between different websites or services is often challenging and time-consuming.

For instance, the Customer Success Department at Local Branch X receives customer requests or bug support tasks that must be manually input into ClickUp\footnote{A project management tool, for futher information refer to \href{https://clickup.com/}{its homepage}}, a project management tool. When customers report bugs, they provide critical information such as the time of occurrence and the type of exceptions encountered. The Customer Success Manager then searches for the exact error in Sentry, an application performance monitoring tool, and forwards this information to the head of the development team. In some cases, the head of the development team creates additional Dev-Tickets in ClickUp with information from Sentry\footnote{A self-hosted and cloud-based application performance monitoring \& error tracking, for further information please refer to \href{https://sentry.io/welcome/}{this} link.}, a labor-intensive process.


%
% Section: Motivation
%
\section{Motivation}\label{sec:intro:motivation}
Addressing the challenges of fragmented workflows and the difficulty of integrating data across multiple platforms is essential for enhancing productivity and efficiency in today's digital landscape. The current manual processes, such as those faced by the Customer Success Department at Local Branch X, highlight the inefficiencies and time-consuming nature of navigating between different services like ClickUp and Sentry.

Creating a dedicated website to handle integration would add another layer of complexity, as users would still need to switch between the website and the services, manually inputting data. A browser extension that facilitates seamless data transfer between services can significantly reduce the time and effort required for such tasks. This would streamline workflows, eliminate the need for manual data entry, and improve overall user productivity. By integrating essential functionalities into a single, coherent interface, the proposed browser extension aims to simplify online activities, enhance user experience, and increase productivity. 

While numerous browser extensions are available, they typically address specific functionalities in isolation, such as bookmarking, password management, or content filtering. There is a notable absence of a unified tool that integrates these essential functions into a single, coherent interface. This lack of integration presents significant challenges in managing multiple online activities, leading to inefficiencies and complexities that hinder user productivity. This situation accentuates the need for an inhouse-developed browser extension that consolidates essential functionalities, streamlines workflows, and simplifies the management of online activities.

%
% Section: Ziele
%
\section{Purpose of the Work}\label{sec:intro:goal}

The objective of this project is to develop a web browser extension that serves as a comprehensive one-stop solution. This extension aims to consolidate various functionalities, streamline workflows, and simplify the management of online activities. To have a better understanding and to provide a clear direction for the development of the browser extension, the following goals have been defined:

\subsection{Functional Criteria}
The browser extension will incorporate several key functionalities:

\begin{itemize}
    \item \textbf{Bookmark Management:}
    The web browser extension will include a robust bookmark management feature that allows users to easily save, organize, and access specific marketing platform web pages. This functionality will help the Customer Success Department quickly access relevant information and resources, enhancing their efficiency and productivity. It ensures that all users who install the extension have access to the same bookmarks without interfering with their existing browser bookmarks. This eliminates the need for employees to sign in with the same Google account (as Google Chrome is the preferred browser at Local Brand X) to access shared bookmarks.

    % TODO: ÜBerlegen mau masukin ini atau engga
    % \item \textbf{Synchronization from ClickUp to MOCO:}
    % The integration of ClickUp with MOCO will enable seamless synchronization of tasks between the project management tool and the ERP system. Tasks created or updated in ClickUp will automatically reflect in MOCO, ensuring that project-related activities are aligned with business processes. This synchronization will minimize the need for manual data entry, reduce errors, and ensure that all team members have access to the latest information, enhancing overall project coordination and efficiency. MOCO will manage accounting, payment invoices for customers, employee salaries, and paychecks directly, as it integrates with other tools like DATEV and ClickUp.

    \item \textbf{Integration of Sentry's Issues Transfer to ClickUp:}
    This feature will facilitate the automatic transfer of issues and error reports from Sentry, a monitoring tool, to ClickUp. When Sentry detects an issue, it will automatically log it as a task in ClickUp, where it can be tracked and managed by the development team. This integration will streamline the error management process, ensure timely resolution of issues, and improve the overall quality and reliability of the software products. It will help the development team quickly identify and resolve issues, reducing downtime and enhancing the user experience, as Sentry provides detailed information about errors, aiding in the rapid identification of root causes.
\end{itemize}

\subsection{Non-Functional Criteria}
The development of the web browser extension will also focus on several non-functional criteria to ensure its effectiveness and usability:

\subsubsection*{Corporate Design Compliant and User-Friendly}\label{subsec:nf-criteria:design}
The proposed extension will adhere to Local Brand X's corporate design guidelines to maintain brand consistency and recognition. Furthermore, the extension will employ a minimalist design approach, reducing unnecessary elements and focusing on core functionalities. This approach aims to streamline user tasks and reduce the time required to perform specific actions. By aligning the interface design with established usability heuristics, the extension will support error prevention, efficient navigation, and clear feedback mechanisms.

\subsubsection*{Performance and Reliability}\label{subsec:nf-criteria:performance-reliability}
On the bookmark management side, the extension will be optimized for performance, ensuring that bookmarks are quickly saved, retrieved, and organized. On the other side the integration of Sentry's issues to ClickUp, the extension will be designed for reliability, ensuring that issues are accurately transferred and tracked without errors and delays. This will help the development team quickly identify and resolve issues, reducing downtime and enhancing the user experience.

\subsubsection*{Security}\label{subsec:nf-criteria:security}
To ensure secure and authorized access to bookmark sync and Sentry issues transfer functionalities, the extension will implement user verification. Only verified users will be able to perform these operations. The user verification process will involve saving user tokens in their settings, allowing the extension to identify and authenticate users. This ensures that all bookmark sync and issues transfer activities are traceable and attributed to specific users. By implementing user verification, the extension enhances security and accountability in managing bookmarks and transferring issues between ClickUp and Sentry.

\subsection*{Data consistency and integrity}\label{subsec:nf-criteria:data-consistency}
The extension will prioritize data consistency and integrity in managing bookmarks. It will implement data validation mechanisms to ensure that only accurate and relevant information is processed and stored. By validating data inputs and outputs, the extension will prevent errors, inconsistencies, and data corruption, ensuring that all bookmarksare correctly saved, retrieved, and transferred. This focus on data consistency and integrity will enhance the reliability and usability of the extension, providing users with accurate and up-to-date information.